Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-19 Submission.Rmd
results section notes

@@

@@

5. *Research Question 3*: Are literature-implicated hiderances consistently rated as job hindrances?

>>>>

> Maybe just do a histogram of standard deviations (overall) or perhaps also by O\*Net dimensions (aim to do this 12/21 in St. Cloud)

@@

> Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O\*Net dimension.

@@

5. *Research Question 3*: Are literature-implicated hindrances consistently rated as job hindrances?

> New graph presents these but need an inferential - maybe ANOVAs

### 2022-12-19 Submission.tex
results section notes

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
\item
  Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
\item
  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\item
  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\item
  \emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
\end{enumerate}

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
\end{enumerate}

\begin{quote}
Maybe just do a histogram of standard deviations (overall) or perhaps also by O*Net dimensions (aim to do this 12/21 in St.~Cloud)
\end{quote}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
\end{enumerate}

\begin{quote}
Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O*Net dimension.
\end{quote}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\item
  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\item
  \emph{Research Question 3}: Are literature-implicated hidrances consistently rated as job hindrances?
\end{enumerate}

\begin{quote}
New graph presents these but need an inferential - maybe ANOVAs
\end{quote}
